Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
Benchmark section reviewed

@@

\subsection{Dataset}
\label{sec:dataset}

Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, 
which features 65 classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
We set the first 45 classes to be known while the remaining 20 are unknown.
For each experiment, 
we report both the best achieved HOS as well as the last reported HOS.
As separation is crucial for the model effectiveness,
 we also report the computer AUROC score for the first part.

>>>>

Lastly, we also exploit the AUROC metric to assess the goodness of the system in separating
the target into a known and unknown part.

@@

\subsection{Benchmark}
\label{sec:dataset}

We evaluate the effectiveness of our proposed method exploiting the {\it Office-Home} {\bf INSERT REFERENCE} benchmark dataset,
widely used to assess the performance for OSDA settings.
The dataset is characterized by four different domains: Art (A), Clipart (C), Product (P) and Real World (R), and
each domain contains the same 65 object class categories.
We underline that the large domain gaps and the number of classes make the benchmark challenging.
For the experiments, we fix the first 45 classes (in alphabetical order) as the known classes ($\mathcal{C}_s$),
and the remaining 20 classes as the unknown ones ($\mathcal{C}_{t \setminus s}$).
For each experiment, we collect the HOS value achieved after the last training epoch of the step 2,
along with the AUROC value computed after the step 1, crucial to assess the goodness
of the system's components responsible for the separation of the target.
